rough outline

### 2022-04-30 outline.Rmd
transfering info on outline

Now, we are going to import the World Population data 
```{r}
world_pop <- read.csv("population_total_long.csv")
```

Let's view the first 6 rows of the data
This dataset covers more than we need, and so we can trim it to the years we need.
```{r}
world_pop2 <- world_pop %>% filter(Year >= 1990 & Year <= 2017)
glimpse(world_pop2)

@@

```{r}
p <- ggplot(deaths_df, aes(x = indoor_deaths, y = outdoor_deaths, text = paste0(country, ", ", year) )) + geom_point()
ggplotly(p)
```

@@

```{r}
hp_countries_population <- world_pop2 %>% 
  filter(Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))

@@

lp_countries_population <- world_pop2 %>% 
  filter(Country.Name %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))

>>>>

Now, we are going to import the World Population data 
```{r}
world_pop <- read.csv("population_total_long.csv")
glimpse(world_pop)
```

Let's split the data into high and low population based on country.
- Low population = high population * .10
```{r}
#Let's compare the first decade 1996-2006 with second decade 2007-2017 
high_pop_countries <- world_pop %>% 
  filter(Year > 1996 & Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia')) %>% 
  group_by(Year)

high_pop_countries

low_pop_countries <- world_pop %>% 
  filter(Year > 1996 & Country.Name %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand'))%>% 
  group_by(Year)

low_pop_countries

@@

```{r}
d <- ggplot(deaths_df, aes(x = indoor_deaths, y = outdoor_deaths, text = paste0(country, ", ", year) )) + geom_point()
ggplotly(d)

#p <- ggplot(world_pop, aes(x = Country.Name, y = Year,  text = paste0(Country.Name, ", ", Year) )) + geom_density()
#ggplotly(p)
```

@@

```{r}
hp_countries_population <- world_pop %>% 
  filter(Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))

@@

lp_countries_population <- world_pop %>% 
  filter(Country.Name %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))
